Setlists: 
- The Eras Tour (Taylor Swift): 37i9dQZF1DX0D996ZXujBy
- Music of the Spheres Tour (Coldplay): 08iPDhTh0lVHhJfb4PlYg7
- Farewell Yellow Brick Road (Elton John): 35xTEkkxtb6HG5Ekrs3Weq
- Divide Tour (Ed Sheeran): 0z7jpWUKsXGJKAr1jPT6TJ
- 360 degrees tour (U2): 2i4RrDDRrjCiZPK7u0mC6l
- Love On Tour (Harry Styles): 0nGAxpspEuFVN41NJtsbqd
- +-=÷x Tour (Ed Sheeran): 54SV4xiry4qbOhWhStFuRk
- Not in This Lifetime... Tour (Guns n Roses): 0JTPSLTRlueygxYUZBZsxK
- Renaissance Tour (Beyonce): 59HEFq5MTQnL15aMiy256x
- A Bigger Bang Tour (The Rolling Stones): 42KCvNJIUSdzAZyZSPSxbE
- No Filter Tour (The Rolling Stones): 2Q1bREtYAvn2bA2VCV2Lws
- A Head Full of Dreams Tour (Coldplay): 7gjMetNaSzrULiFfg82o7K
- Summer Carnival (P!nk): 5s0m7X05Le1APAVOMXozVS
- The Wall Live (Roger Waters): 4bwDALUCGomY6xRJRvo3Un
- Black Ice World Tour (AC/DC): 6yMtPXxICqPJzqnX11dnvD ***includes encore***
- WorldWired Tour (Metallica): 5fkZFNe5tSzZE3WrxwxzhC
- Sticky & Sweet Tour (Madonna): 0Y4Kj7njDZ6An4SSi9sSr2
- Beautiful Trauma World Tour (P!nk): 0IOqgNJX3k9aPeLMIYhpxh
- The Joshua Tree Tours 2017 & 2019 (U2): 4jpUeNiMgahRfNlAde3Shw
- Vertigo Tour (U2): 2TDIyyayjko0cnS00459ui


Artists: 
- Taylor Swift: 06HL4z0CvFAxyc27GXpf02
- Coldplay: 4gzpq5DPGxSnKTe4SA8HAU
- Elton John: 3PhoLpVuITZKcymswpck5b
- Ed Sheeran: 6eUKZXaKkcviH0Ku9w2n3V
- U2: 51Blml2LZPmy7TTiAg47vQ
- Harry Styles: 6KImCVD70vtIoJWnq6nGn3
- Guns N' Roses: 3qm84nBOXUEQ2vnTfUTTFC
- Beyonce: 6vWDO969PvNqNYHIOW5v0m
- The Rolling Stones: 22bE4uQ6baNwSHPVcDxLCe
- P!nk: 1KCSPY1glIKqW2TotWuXOR
- Roger Waters: 40DqL6Tv84cKT2pH2NMs9r
- AC/DC: 711MCceyCBcFnzjGY4Q7Un
- Metallica: 2ye2Wgw4gimLv2eAKyk1NB
- Madonna: 6tbjWDEIzxoDsBA1FuhfPW


```{r}
library(spotifyr)
library(dplyr)
library(purrr)
library(tidyverse)
library(rlang)
```

```{r}
# fill in with personal client_ID and client_secret
Sys.setenv(SPOTIFY_CLIENT_ID = '')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '')

access_token <- get_spotify_access_token()
```

Logging all of our spotifyIDs into one vector:

```{r}
playlist_ids <- c(
  "37i9dQZF1DX0D996ZXujBy", "08iPDhTh0lVHhJfb4PlYg7", "35xTEkkxtb6HG5Ekrs3Weq",
  "0z7jpWUKsXGJKAr1jPT6TJ", "2i4RrDDRrjCiZPK7u0mC6l", "0nGAxpspEuFVN41NJtsbqd",
  "54SV4xiry4qbOhWhStFuRk", "0JTPSLTRlueygxYUZBZsxK", "59HEFq5MTQnL15aMiy256x", 
  "42KCvNJIUSdzAZyZSPSxbE", "42KCvNJIUSdzAZyZSPSxbE", "2Q1bREtYAvn2bA2VCV2Lws",
  "7gjMetNaSzrULiFfg82o7K", "5s0m7X05Le1APAVOMXozVS", "4bwDALUCGomY6xRJRvo3Un",
  "6yMtPXxICqPJzqnX11dnvD", "5fkZFNe5tSzZE3WrxwxzhC", "0IOqgNJX3k9aPeLMIYhpxh", 
  "4jpUeNiMgahRfNlAde3Shw", "2TDIyyayjko0cnS00459ui")

artist_ids <- c(
  "06HL4z0CvFAxyc27GXpf02", "4gzpq5DPGxSnKTe4SA8HAU", "3PhoLpVuITZKcymswpck5b", "6eUKZXaKkcviH0Ku9w2n3V", 
  "51Blml2LZPmy7TTiAg47vQ", "6KImCVD70vtIoJWnq6nGn3", "3qm84nBOXUEQ2vnTfUTTFC", "6vWDO969PvNqNYHIOW5v0m", 
  "22bE4uQ6baNwSHPVcDxLCe", "1KCSPY1glIKqW2TotWuXOR", "40DqL6Tv84cKT2pH2NMs9r", "711MCceyCBcFnzjGY4Q7Un", 
  "2ye2Wgw4gimLv2eAKyk1NB", "6tbjWDEIzxoDsBA1FuhfPW"
)
```


```{r}
wrangle_data_func <- function(spotifyid){
  get_playlist_audio_features(
    "spotify", 
    playlist_uris = spotifyid, 
    access_token # spotify developer credentials
    ) |>
  # take out unnecessary columns
  select(-c(playlist_owner_id, added_at, is_local, primary_color, added_by.href, added_by.id, added_by.type, added_by.uri, 
            added_by.external_urls.spotify,track.preview_url, track.available_markets, track.type, track.episode, track.track,
            track.disc_number, track.href, track.is_local, track.album.available_markets, track.album.type, track.album.album_type,
            track.album.href, track.album.release_date_precision, track.album.artists, track.album.external_urls.spotify,
            track.external_ids.isrc, track.external_urls.spotify, video_thumbnail.url )) |>
  # create new cols to tell us where we are in the setlist
  mutate(setlist_song_num = row_number(),
         prop_thru_set = setlist_song_num / n())
}

# as list of separate data, use `map_df()` if want one big list
all_playlists <- map(playlist_ids, wrangle_data_func)
```

```{r}
all_data <- map_df(playlist_ids, wrangle_data_func)
```


### Visualize audio features
```{r}
visualize_feature <- function(data, feature) {
  data |>
    ggplot(aes(x = prop_thru_set, y = data[[feature]])) + 
    geom_point() +
    geom_smooth(se = FALSE) + 
    # add geom_hline for mean feature value for artist
    xlab("Set Progress") + 
    ylab(feature) + 
    facet_wrap(~ playlist_name)
}
```

```{r}
visualize_feature(all_data, "danceability")
```

```{r}
get_artist_mean_features <- function(artist_df, feature) {
  mean(artist_df[[feature]])
}

get_artist_mean_feature(get_artist_audio_features("Taylor Swift"), "energy")
```

# TODO: make a df of artist mean audio features (ex. mean danceability across all the artist's songs) to compare set danceability to average? 




